NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-26 paper/pipeline.tex
update captions

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipeline}
 \caption{Language Inference Model Pipeline.}
\label{fig:modelPipeline}
\end{figure}

\section{The p-NLI System}
In this section, we describe the p-NLI system.

% Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly examine the mechanism of the model.
%
Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.

>>>>

\subsection{Pipeline View}

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipelineView}
 \caption{
Visual representation of the three stages (encoder, attention, classifier) model. In the proposed tool, we allow the model parameter to be updated to fix a prediction error. The pipeline view, by showing the aggregated gradient distribution, inform the user about the how different part of the model response to the optimization.
%
The optimization parameters is shown in (a), each of the stages is illustrated in (b), where the user can click on the parameter bar to enable or disable its update (the legend about its state is shown in (d) ). In (c), we select whether if we want to use current update setting as display or try all the configuration combination (i.e., update for each stage can be enabled or disabled).
 }
\label{fig:modelPipeline}
\end{figure}

\subsubsection{Margin-Infused Relaxed Algorithm (MIRA)}
the mira loss is $|w' - w|^2 + C * J(w')$

### 2018-03-26 paper/predSummary.tex
update sentence view
update captions

\subsection{All Pairs Summary View}
\label{sec:allPairs}
Since we can only focus on one individual example at a time for detail analysis,
how to pick an single pair of sentence from the development or test dataset (for the SNLI dataset, each of the these set consists of close to $10k$ examples) is an obvious challenge.
%
In addition, we also want to obtain certain high-level understand of how the whole set behave, beyond the information the prediction accuracy provide.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{summaryView}
 \caption{Explore the full development set and examine their prediction result and sensitivity.}
\label{fig:modelPipeline}
\end{figure}

%The all pair
\begin{itemize}
\item How to go from 10k pair to one pair
\item What constitute interesting example
\item How to get a sense of overall prediction result
\end{itemize}

>>>>

\subsection{All Predictions Summary View}
\label{sec:allPairs}
Since we can only focus on one individual example at a time for detail analysis,
how to pick a single pair of sentence from the development or test dataset (for the SNLI dataset, each of the these set consists of close to $10k$ examples) is an obvious challenge.
%
Beside the selection task, generate visual summarization there we also want to obtain certain high-level understand of how the whole set behave, beyond the information the prediction accuracy provide.

%treemap for prediction
We utilized a treemap (a) to encode the ground truth label and the model prediction generated by the
By click on the treemap cell, we can narrow down the selection by focus on specific senarios.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{summaryView}
 \caption{
Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select example of interests.
We summarize all the prediction results in (a), where the green block indicates correct predictions, and orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
%
The user can select the treemap to focus on the specific type of senarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
The selection can be further narrowed down by select the bin in the histogram.
In (c) and (d), each point corresponds to one prediction.
 }
\label{fig:modelPipeline}
\end{figure}

%The all pair
% \begin{itemize}
% \item How to go from 10k pair to one pair
% \item What constitute interesting example
% \item How to get a sense of overall prediction result
% \end{itemize}

### 2018-03-26 paper/prediction.tex
update paper structure
add sections structure
update task
update captions

\subsection{User-Guided Prediction Update}

\subsubsection{Margin-Infused Relaxed Algorithm (MIRA)}
the mira loss is $|w' - w|^2 + C * J(w')$

>>>>

\subsection{Prediction View}

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.85\linewidth]{predictionView}
 \caption{
 In the prediction view, the prediciton probability (the probability of being neutral, contradict, and entailment) is encoded as barycentric coordinate system in an triangle.
 The prediction result for the original sentence pair is represented by larger yellow dot) and their perturbations are illustrated by smaller grey dots.
 A density contour of the prediction is computed to emphasis the highly cluttered areas and distinguish the outliers.
 %How domain experts conduct error analysis on the model.
 }
\label{fig:modelPipeline}
\end{figure}

### 2018-03-26 paper/sentence.tex
update captions

\subsection{Sentence View}
To start an exploration cycle, the experts need to examine the premise and hypothesis sentence the current example. 
As illustrated in Fig.~\ref{fig:modelPipeline}, the sentence view shows the premise and hypothesis sentence in (c) and (d).
%
To facilitate the analysis task (\textbf{T1}), we employ an automate sentence perturbation scheme that replaces nous and verb by their synonymous in the wordNet~\cite{Miller1995} (the standard lexical database for NLP applications).
%
When perturbation is applied to either of the sentences, the replaced words are highlight in blue (see Fig~\ref{fig:modelPipeline}(e) ) to indicate the modification to the original sentence.
%
%%% sentence perturbation %%%%
In addition, the user can type any sentences or modified existing text in the (c) and (d) to accommodate customized input when expert want to conduct quick experiment or when the automatic perturbation does not meet expectations.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.85\linewidth]{sentenceView}
 \caption{Sentence view shows the premise and the hypothesis sentence pair.}
\label{fig:modelPipeline}
\end{figure}

\begin{itemize}
\item Examine perturbed pair
\item See which word is perturbed in a sentence
\item Add to existing example collection
\end{itemize}

>>>>

\subsection{Sentence View}
To start an exploration cycle, the experts need to examine the premise and hypothesis sentence the current example. 
As illustrated in Fig.~\ref{fig:modelPipeline}, the sentence view shows the premise and hypothesis sentence in (c) and (d).
%
To facilitate the analysis task (\textbf{T1}), we employ an automate sentence perturbation scheme that replaces nous and verb by their synonymous in the wordNet~\cite{Miller1995} (the standard lexical database for NLP applications).
%
When perturbation is applied to either of the sentences, the replaced words are highlight in blue (see Fig~\ref{fig:modelPipeline}(e) ) to indicate the modification to the original sentence.
%
In (a), \emph{Predict} and \emph{Predict All}, each corresponds to predict the current displayed sentence pairs, or predict all combinations of perturbed premise and hypothesis, provided there is only one perturbation per sentence pair (i.e., we use original premise if hypothesis is perturbed, or use original hypothesis if premise is perturbed). 
%%% sentence perturbation %%%%
In (b), previous explored original sentence are stored in the dropdown list that allow the user to revisit previous examined sentence.
In addition, the user can type any sentences or modified existing text in the (c) and (d) to accommodate customized input when expert want to conduct quick experiment or when the automatic perturbation does not meet expectations.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.95\linewidth]{sentenceView}
 \caption{
Sentence view shows the premise (c) and the hypothesis (d) sentence pair. The word that replaces the original text is highlight in blue, as illustrated in (e)
In (a), \emph{Predict} and \emph{Predict All}, each corresponds to predict the current displayed sentence pairs, or predict all combinations of perturbed premise and hypothesis.
In (b), previous explored original sentence are stored in the dropdown list that allow the user to revisit previous examined sentence.
 }
\label{fig:modelPipeline}
\end{figure}

%\begin{itemize}
%\item Examine perturbed pair
%\item See which word is perturbed in a sentence
%\item Add to existing example collection
%\end{itemize}
